---
title: "Stereotypes about first names"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

This website presents stereotypic ratings of first names, as judged by
German participants under laboratory conditions. For detailed
information about the methodology, please refer to [Speckmann and Wingen (2023)](https://econtent.hogrefe.com/doi/full/10.1027/2151-2604/a000515) . It is important to note that these ratings were provided by a
non-representative sample of students and do not reflect actual
attributes of individuals bearing these names.

```{r loading data and wrangling, echo = F, include = F}
library(readr)
library(tidyverse)
library(DT)
library(plotly)


data <- read_csv("name_ratings_lab.csv")
#reorder and name

data <- data |> 
  select(-number, name, everything()) |> 
  rename(judged_gender = gender) |> 
  dplyr::arrange(-modern)

# Recoding 'gender' and rounding all numerical values
data <- data %>%
  mutate(
    judged_gender = recode(judged_gender, `1` = "female", `2` = "male"),
    across(where(is.numeric), ~round(.x, digits = 2))
  )


```

```{r table, echo = F}

# Create an interactive DataTable
datatable(data, options = list(pageLength = 25, autoWidth = TRUE))


```

# Licence

Data: "name_ratings_lab.csv" by \[Speckmann, Felix & Wingen, Tobias\], [PsychArchives](https://psycharchives.org/en/item/3e458a24-b08b-4d1f-8a72-148b78ba2331), licensed under CC BY 4.0 ([License](https://creativecommons.org/licenses/by/4.0/#ref-appropriate-credit)).

Paper: Speckmann, F., & Wingen, T. (2023). Same Question, Different Answers?. *Zeitschrift für Psychologie. 231*(1), 30-38 https://doi.org/10.1027/2151-2604/a000515
